Measurement of nuclear excitation functions for proton induced reactions (E$_{\text{p}}$ = 40 -- 90 MeV) on natural Nb and Cu

### 2017-12-08 nb_px_paper/nb_px_paper.tex
Finished section 3

The propagated uncertainty in proton fluence is calculated as the quadrature sum of the uncertainty in quantified EoB activity, uncertainty in the duration of irradiation (conservatively estimated at 60 s, to account for any transient changes in beam current), uncertainty in foil areal density, uncertainty in monitor product half-life (included, but normally negligible), uncertainty in IAEA recommended cross section, and uncertainty in proton fluence.
Of these, the first four contributions are all easily quantified in the preparation and execution of a stacked target irradiation;  the last two contributions prove to be more nuanced, however.
The uncertainty in proton fluence for irradiated monitor foils is derived from statistical uncertainty in the modeling of proton transport in the stack irradiation, discussed in \autoref{sec:proton_transport}.
The uncertainty in IAEA recommended cross section values must be estimated indirectly, as no uncertainty in the  recommended cross sections is provided in the current IAEA evaluation.
Fortunately, the recommended cross section values for each monitor reaction tend to match one of the   selected experimental data sets used in their evaluation almost perfectly.
Since these data sets have listed uncertainties in the original manuscripts, uncertainties in  IAEA recommended cross section values have been estimated by the uncertainty in the data set most closely matching the  IAEA recommended  values.
For the monitor reactions employed in this work, these data sets are G. Steyn (1990) for  \ce{^{nat}Al}(p,x)\ce{^{22}Na} \textred{(insert Steyn citation here)}, M. Uddin (2004) for \ce{^{nat}Al}(p,x)\ce{^{24}Na} \cite{Uddin2004}, and S. Mills (1992) for \ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} \cite{Mills1992}.

@@

XXXXXX

\comment{Double check this equation from my scratch work at LBL}

@@

\subsection{Systematic uncertainties}

XXXXXX

@@

XXXXXX

>>>>

The propagated uncertainty in proton fluence is calculated as the quadrature sum of the uncertainty in quantified EoB activity, uncertainty in the duration of irradiation (conservatively estimated at 60 s, to account for any transient changes in beam current), uncertainty in foil areal density, uncertainty in monitor product half-life (included, but normally negligible), uncertainty in IAEA recommended cross section, and uncertainty in differential proton fluence.
Of these, the first four contributions are all easily quantified in the preparation and execution of a stacked target irradiation;  the last two contributions prove to be more nuanced, however.
The uncertainty in proton fluence for irradiated monitor foils is derived from statistical uncertainty in the modeling of proton transport in the stack irradiation, discussed in \autoref{sec:proton_transport}.
The uncertainty in IAEA recommended cross section values must be estimated indirectly, as no uncertainty in the  recommended cross sections is provided in the current IAEA evaluation.
Fortunately, the recommended cross section values for each monitor reaction tend to match one of the   selected experimental data sets used in their evaluation almost perfectly.
Since these data sets have listed uncertainties in the original manuscripts, uncertainties in  IAEA recommended cross section values have been estimated by the uncertainty in the data set most closely matching the  IAEA recommended  values.
For the monitor reactions employed in this work, these data sets are G. Steyn (1990) for  \ce{^{nat}Al}(p,x)\ce{^{22}Na} \textred{(insert Steyn citation here)}, M. Uddin (2004) for \ce{^{nat}Al}(p,x)\ce{^{24}Na} \cite{Uddin2004}, and S. Mills (1992) for \ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} \cite{Mills1992}.

@@

Using the quantified EoB activities along with the variance-minimized proton fluence, it is possible to calculate the final cross sections for the various Nb(p,x) reactions observed in decay spectroscopy.
While thin ($\approx$ 22 mg/cm$^2$) Nb foils were irradiated to minimize the energy width of these cross section measurements, it is important to note that all cross sections reported here are flux-averaged cross sections, over the energy distribution subtended by each foil, as seen in \autoref{fig:Nb_ptallies}.
For both the cumulative and independent activities quantified, cross sections were calculated as:
\begin{equation}
\sigma = \dfrac{A_0 }{\rho \Delta r I \pp{1-e^{-\lambda \Delta t}} }
\end{equation}
where $A_0$ is the EoB activity for the monitor reaction product, $I$ is the proton current, $\rho \Delta r$ is the foil's areal density, $\lambda$ is the monitor reaction product's decay constant, and $\Delta t$ is the length of irradiation.
The propagated uncertainty in cross section is calculated as the quadrature sum of the uncertainty in quantified EoB activity, uncertainty in the duration of irradiation (conservatively estimated at 60 s, to account for any transient changes in beam current), uncertainty in foil areal density, uncertainty in monitor product half-life (included, but normally negligible),  and uncertainty in proton current (quantified in the $2\sigma$ confidence interval in \autoref{fig:fluence_plot}).

@@

% \subsection{Systematic uncertainties}
% 
% XXXXXX

@@

After irradiation, all foils were confirmed to still be sealed inside their Kapton packets, verifying that no activation products were lost due to packet failure and dispersal.
In addition, each activated foil had a small \enquote{blister} under the Kapton tape layer, caused by a combination of thermal swelling and the formation of short-lived beta activities.
This blister   shows the location where the primary proton beam was incident upon the foil, and serves to build confidence that the beam was not stopped before reaching the last foil in the stack.
Based on the \ce{^{nat}Al}(p,x)\ce{^{24}Na}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reactions used to determine the average fluence at each energy position (seen in \autoref{fig:fluence_plot}), a fluence of 202.2$\pm$5.4 nAh was calculated to be incident upon the target stack, which shows excellent agreement with the nominal fluence of 205.9 nAh based on IPF upstream current monitors.
This incident fluence dropped by approximately 8.1\% to  185.9 $\pm$3.4 nAh over the length of the target stack, which is consistent with similar measurements at IPF in the past \cite{Graves2016}.
This loss of fluence is due to a combination of beam utilization for the various (p,x) reactions throughout the target stack, as well as large-angle deflections (primarily in the 6061 aluminum degraders) from scattering of the beam.

Using the final proton fluence at each energy position, cross sections for  \ce{^{51}Cr},  \ce{^{52g}Mn}, \ce{^{52m}Mn}, \ce{^{54}Mn}, \ce{^{55}Co}, \ce{^{56}Ni}, \ce{^{57}Ni}, \ce{^{57}Co},  \ce{^{58g}Co}, \ce{^{58m}Co}, \ce{^{59}Fe}, \ce{^{60}Co}, \ce{^{61}Cu}, and \ce{^{64}Cu} were extracted for (p,x) reactions  on \ce{^{nat}Cu} foils in the 40 - 90 MeV region, as recorded in \autoref{tab:cu_rp_table}.
For  (p,x) reactions on \ce{^{nat}Nb} foils, the (p,x) cross sections for \ce{^{82m}Rb}, \ce{^{83}Sr}, \ce{^{85g}Y}, \ce{^{85m}Y}, \ce{^{86}Zr}, \ce{^{86}Y}, \ce{^{87}Zr}, \ce{^{87g}Y}, \ce{^{87m}Y}, \ce{^{88}Zr}, \ce{^{88}Y}, \ce{^{89g}Nb}, \ce{^{89m}Nb}, \ce{^{89}Zr}, \ce{^{90}Mo}, \ce{^{90}Nb}, \ce{^{91m}Nb}, \ce{^{92m}Nb}, and \ce{^{93m}Mo} were extracted, as recorded in \autoref{tab:nb_rp_table}.
In addition, as there exist a number of isomers with radioactive ground states in these mass regions,  independent measurements of isomer-to-ground-state branching ratios for \ce{^{52m/g}Mn},\ce{^{58m/g}Co},\ce{^{85m/g}Y},\ce{^{87m/g}Y}, and \ce{^{89m/g}Nb} were  extracted from these data as well, which are recorded in \autoref{tab:ibr_table}.
Comparisons  of the measured cross sections and isomer branching ratios with literature data (retrieved from EXFOR \cite{Otuka2014272}) are seen in the figures of \ref{fit_figures} and \ref{ibr_figures}.
The propagated uncertainty in these cross sections varies widely based on the reaction product in question, with the major components  arising from uncertainty in EoB activity ($\pm$1-7\%), proton fluence ($\pm$2-3\%), and foil areal density ($\pm$0.1-0.6\%).

% % Please add the following required packages to your document preamble:
% % \usepackage{booktabs}
% \begin{table}
% \centering
% \caption{My caption}
% \label{my-label}
% \small
% \begin{tabular}{@{}lllllll@{}}
% \toprule
% E$_\text{p}$ (MeV) & $89.37^{+0.47}_{-0.45}$ & $79.55^{+0.68}_{-0.64}$ & $69.70^{+0.90}_{-0.85}$ & $61.07^{+1.05}_{-0.98}$ & $51.51^{+1.25}_{-1.21}$ & $40.34^{+1.58}_{-1.55}$ \\ \midrule
% 82mRb      & $2.39\pm0.18$           & \hrulefill              & \hrulefill              & \hrulefill              & \hrulefill              & \hrulefill              \\
% 83Sr       & $3.88\pm0.56$           & $4.63\pm0.34$           & $3.42\pm0.32$           & \hrulefill              & \hrulefill              & \hrulefill              \\
% 85cum Y    & $13.31\pm0.30$          & $7.28\pm0.44$           & $2.06\pm0.12$           & \hrulefill              & \hrulefill              & \hrulefill              \\
% 85gY       & $2.286\pm0.057$         & $2.010\pm0.150$         & $0.545\pm0.030$         & \hrulefill              & \hrulefill              & \hrulefill              \\
% 85mY       & $11.03\pm0.30$          & $5.27\pm0.42$           & $1.52\pm0.12$           & \hrulefill              & \hrulefill              & \hrulefill              \\
% 86Zr       & $12.25\pm0.32$          & $17.63\pm0.44$          & $18.86\pm0.43$          & $6.00\pm0.15$           & \hrulefill              & \hrulefill              \\
% 86Y        & $32.25\pm0.89$          & $40.30\pm1.07$          & $39.02\pm1.00$          & $13.22\pm0.34$          & \hrulefill              & \hrulefill              \\
% 87Zr       & $45.82\pm5.82$          & $27.09\pm1.72$          & $31.46\pm1.49$          & $48.55\pm2.92$          & $37.66\pm1.58$          & $1.13\pm0.10$           \\
% 87cum Y    & $106.26\pm5.81$         & $52.92\pm1.70$          & $59.63\pm1.47$          & $87.77\pm2.90$          & $66.29\pm1.56$          & $2.93\pm0.10$           \\
% 87gY       & $27.03\pm5.45$          & $7.15\pm1.19$           & $6.41\pm0.55$           & $5.65\pm2.13$           & $2.59\pm0.45$           & $0.949\pm0.045$         \\
% 87mY       & $79.23\pm2.01$          & $45.78\pm1.22$          & $53.22\pm1.37$          & $82.12\pm1.97$          & $63.70\pm1.49$          & $1.98\pm0.09$           \\
% 88Zr       & $153.69\pm3.93$         & $140.02\pm3.48$         & $60.99\pm1.70$          & $20.65\pm0.49$          & $33.16\pm0.97$          & $65.82\pm1.32$          \\
% 88Y        & $16.64\pm0.76$          & $12.85\pm0.60$          & $7.81\pm0.61$           & $2.83\pm0.20$           & $9.05\pm1.33$           & $9.96\pm0.33$           \\
% 89cum Nb   & \hrulefill              & \hrulefill              & $175.52\pm12.44$        & $208.99\pm4.33$         & \hrulefill              & \hrulefill              \\
% 89gNb      & \hrulefill              & \hrulefill              & $141.58\pm12.28$        & $181.73\pm4.08$         & \hrulefill              & \hrulefill              \\
% 89mNb      & \hrulefill              & \hrulefill              & $33.94\pm1.97$          & $27.26\pm1.45$          & \hrulefill              & \hrulefill              \\
% 89Zr       & $203.76\pm5.32$         & $235.36\pm6.57$         & $287.50\pm6.76$         & $250.32\pm5.77$         & $54.63\pm1.15$          & $15.61\pm0.31$          \\
% 90Mo       & $20.57\pm0.68$          & $25.58\pm0.76$          & $33.75\pm0.90$          & $60.38\pm1.86$          & $120.28\pm2.93$         & $24.38\pm0.71$          \\
% 90Nb       & $152.93\pm4.72$         & $169.31\pm4.78$         & $204.70\pm5.79$         & $265.19\pm7.77$         & $363.35\pm9.78$         & $165.16\pm4.54$         \\
% 91mNb      & \hrulefill              & \hrulefill              & \hrulefill              & \hrulefill              & \hrulefill              & $66.96\pm4.16$          \\
% 92mNb      & $42.18\pm1.15$          & $45.74\pm1.16$          & $48.75\pm1.21$          & $51.59\pm1.34$          & $54.49\pm1.37$          & $60.36\pm1.23$          \\
% 93mMo      & $0.93\pm0.18$           & $1.25\pm0.13$           & $1.58\pm0.22$           & $1.80\pm0.12$           & $1.83\pm0.10$           & $2.010\pm0.084$         \\ \bottomrule
% \end{tabular}
% \end{table}
% 
% % Please add the following required packages to your document preamble:
% % \usepackage{booktabs}
% \begin{table}[]
% \centering
% \caption{My caption}
% \label{my-label}
% \small
% \begin{tabular}{@{}llllllll@{}}
% \toprule
%       &            & \multicolumn{6}{c}{Production cross section (mb)}                                                                                                         \\ 
%       & E\_p (MeV) & $89.37^{+0.47}_{-0.45}$ & $79.55^{+0.68}_{-0.64}$ & $69.70^{+0.90}_{-0.85}$ & $61.07^{+1.05}_{-0.98}$ & $51.51^{+1.25}_{-1.21}$ & $40.34^{+1.58}_{-1.55}$ \\ \midrule
% 82mRb & $\sigma_c$ & $2.39\pm0.18$           & \hrulefill              & \hrulefill              & \hrulefill              & \hrulefill              & \hrulefill              \\
% 83Sr  & $\sigma_c$ & $3.88\pm0.56$           & $4.63\pm0.34$           & $3.42\pm0.32$           & \hrulefill              & \hrulefill              & \hrulefill              \\
% 85 Y  & $\sigma_c$ & $13.31\pm0.30$          & $7.28\pm0.44$           & $2.06\pm0.12$           & \hrulefill              & \hrulefill              & \hrulefill              \\
% 85gY  & $\sigma_i$ & $2.286\pm0.057$         & $2.010\pm0.150$         & $0.545\pm0.030$         & \hrulefill              & \hrulefill              & \hrulefill              \\
% 85mY  & $\sigma_i$ & $11.03\pm0.30$          & $5.27\pm0.42$           & $1.52\pm0.12$           & \hrulefill              & \hrulefill              & \hrulefill              \\
% 86Zr  & $\sigma_c$ & $12.25\pm0.32$          & $17.63\pm0.44$          & $18.86\pm0.43$          & $6.00\pm0.15$           & \hrulefill              & \hrulefill              \\
% 86Y   & $\sigma_c$ & $32.25\pm0.89$          & $40.30\pm1.07$          & $39.02\pm1.00$          & $13.22\pm0.34$          & \hrulefill              & \hrulefill              \\
% 87Zr  & $\sigma_c$ & $45.82\pm5.82$          & $27.09\pm1.72$          & $31.46\pm1.49$          & $48.55\pm2.92$          & $37.66\pm1.58$          & $1.13\pm0.10$           \\
% 87 Y  & $\sigma_c$ & $106.26\pm5.81$         & $52.92\pm1.70$          & $59.63\pm1.47$          & $87.77\pm2.90$          & $66.29\pm1.56$          & $2.93\pm0.10$           \\
% 87gY  & $\sigma_i$ & $27.03\pm5.45$          & $7.15\pm1.19$           & $6.41\pm0.55$           & $5.65\pm2.13$           & $2.59\pm0.45$           & $0.949\pm0.045$         \\
% 87mY  & $\sigma_i$ & $79.23\pm2.01$          & $45.78\pm1.22$          & $53.22\pm1.37$          & $82.12\pm1.97$          & $63.70\pm1.49$          & $1.98\pm0.09$           \\
% 88Zr  & $\sigma_c$ & $153.69\pm3.93$         & $140.02\pm3.48$         & $60.99\pm1.70$          & $20.65\pm0.49$          & $33.16\pm0.97$          & $65.82\pm1.32$          \\
% 88Y   & $\sigma_c$ & $16.64\pm0.76$          & $12.85\pm0.60$          & $7.81\pm0.61$           & $2.83\pm0.20$           & $9.05\pm1.33$           & $9.96\pm0.33$           \\
% 89 Nb & $\sigma_c$ & \hrulefill              & \hrulefill              & $175.52\pm12.44$        & $208.99\pm4.33$         & \hrulefill              & \hrulefill              \\
% 89gNb & $\sigma_i$ & \hrulefill              & \hrulefill              & $141.58\pm12.28$        & $181.73\pm4.08$         & \hrulefill              & \hrulefill              \\
% 89mNb & $\sigma_i$ & \hrulefill              & \hrulefill              & $33.94\pm1.97$          & $27.26\pm1.45$          & \hrulefill              & \hrulefill              \\
% 89Zr  & $\sigma_c$ & $203.76\pm5.32$         & $235.36\pm6.57$         & $287.50\pm6.76$         & $250.32\pm5.77$         & $54.63\pm1.15$          & $15.61\pm0.31$          \\
% 90Mo  & $\sigma_c$ & $20.57\pm0.68$          & $25.58\pm0.76$          & $33.75\pm0.90$          & $60.38\pm1.86$          & $120.28\pm2.93$         & $24.38\pm0.71$          \\
% 90Nb  & $\sigma_c$ & $152.93\pm4.72$         & $169.31\pm4.78$         & $204.70\pm5.79$         & $265.19\pm7.77$         & $363.35\pm9.78$         & $165.16\pm4.54$         \\
% 91mNb & $\sigma_c$ & \hrulefill              & \hrulefill              & \hrulefill              & \hrulefill              & \hrulefill              & $66.96\pm4.16$          \\
% 92mNb & $\sigma_c$ & $42.18\pm1.15$          & $45.74\pm1.16$          & $48.75\pm1.21$          & $51.59\pm1.34$          & $54.49\pm1.37$          & $60.36\pm1.23$          \\
% 93mMo & $\sigma_c$ & $0.93\pm0.18$           & $1.25\pm0.13$           & $1.58\pm0.22$           & $1.80\pm0.12$           & $1.83\pm0.10$           & $2.010\pm0.084$         \\ \bottomrule
% \end{tabular}
% \end{table}
% 
% % Please add the following required packages to your document preamble:
% % \usepackage{booktabs}
% \begin{table}[]
% \centering
% \caption{My caption}
% \label{my-label}
% \small
% \begin{tabular}{@{}llllllll@{}}
% \toprule
%       &            & \multicolumn{6}{c}{Production cross section (mb)}                                                                                                         \\ \cmidrule(l){3-8} 
%       & E\_p (MeV) & $89.37^{+0.47}_{-0.45}$ & $79.55^{+0.68}_{-0.64}$ & $69.70^{+0.90}_{-0.85}$ & $61.07^{+1.05}_{-0.98}$ & $51.51^{+1.25}_{-1.21}$ & $40.34^{+1.58}_{-1.55}$ \\ \midrule
% \ce{^{82m}Rb} & $\sigma_c$ & $2.39\pm0.18$           & \hrulefill              & \hrulefill              & \hrulefill              & \hrulefill              & \hrulefill              \\
% 83Sr  & $\sigma_c$ & $3.88\pm0.56$           & $4.63\pm0.34$           & $3.42\pm0.32$           & \hrulefill              & \hrulefill              & \hrulefill              \\
% 85 Y  & $\sigma_c$ & $13.31\pm0.30$          & $7.28\pm0.44$           & $2.06\pm0.12$           & \hrulefill              & \hrulefill              & \hrulefill              \\
% 85gY  & $\sigma_i$ & $2.286\pm0.057$         & $2.010\pm0.150$         & $0.545\pm0.030$         & \hrulefill              & \hrulefill              & \hrulefill              \\
% 85mY  & $\sigma_i$ & $11.03\pm0.30$          & $5.27\pm0.42$           & $1.52\pm0.12$           & \hrulefill              & \hrulefill              & \hrulefill              \\
% 86Zr  & $\sigma_c$ & $12.25\pm0.32$          & $17.63\pm0.44$          & $18.86\pm0.43$          & $6.00\pm0.15$           & \hrulefill              & \hrulefill              \\
% 86Y   & $\sigma_c$ & $32.25\pm0.89$          & $40.30\pm1.07$          & $39.02\pm1.00$          & $13.22\pm0.34$          & \hrulefill              & \hrulefill              \\
% 87Zr  & $\sigma_c$ & $45.82\pm5.82$          & $27.09\pm1.72$          & $31.46\pm1.49$          & $48.55\pm2.92$          & $37.66\pm1.58$          & $1.13\pm0.10$           \\
% 87 Y  & $\sigma_c$ & $106.26\pm5.81$         & $52.92\pm1.70$          & $59.63\pm1.47$          & $87.77\pm2.90$          & $66.29\pm1.56$          & $2.93\pm0.10$           \\
% 87gY  & $\sigma_i$ & $27.03\pm5.45$          & $7.15\pm1.19$           & $6.41\pm0.55$           & $5.65\pm2.13$           & $2.59\pm0.45$           & $0.949\pm0.045$         \\
% 87mY  & $\sigma_i$ & $79.23\pm2.01$          & $45.78\pm1.22$          & $53.22\pm1.37$          & $82.12\pm1.97$          & $63.70\pm1.49$          & $1.98\pm0.09$           \\
% 88Zr  & $\sigma_c$ & $153.69\pm3.93$         & $140.02\pm3.48$         & $60.99\pm1.70$          & $20.65\pm0.49$          & $33.16\pm0.97$          & $65.82\pm1.32$          \\
% 88Y   & $\sigma_c$ & $16.64\pm0.76$          & $12.85\pm0.60$          & $7.81\pm0.61$           & $2.83\pm0.20$           & $9.05\pm1.33$           & $9.96\pm0.33$           \\
% 89 Nb & $\sigma_c$ & \hrulefill              & \hrulefill              & $175.52\pm12.44$        & $208.99\pm4.33$         & \hrulefill              & \hrulefill              \\
% 89gNb & $\sigma_i$ & \hrulefill              & \hrulefill              & $141.58\pm12.28$        & $181.73\pm4.08$         & \hrulefill              & \hrulefill              \\
% 89mNb & $\sigma_i$ & \hrulefill              & \hrulefill              & $33.94\pm1.97$          & $27.26\pm1.45$          & \hrulefill              & \hrulefill              \\
% 89Zr  & $\sigma_c$ & $203.76\pm5.32$         & $235.36\pm6.57$         & $287.50\pm6.76$         & $250.32\pm5.77$         & $54.63\pm1.15$          & $15.61\pm0.31$          \\
% 90Mo  & $\sigma_c$ & $20.57\pm0.68$          & $25.58\pm0.76$          & $33.75\pm0.90$          & $60.38\pm1.86$          & $120.28\pm2.93$         & $24.38\pm0.71$          \\
% 90Nb  & $\sigma_c$ & $152.93\pm4.72$         & $169.31\pm4.78$         & $204.70\pm5.79$         & $265.19\pm7.77$         & $363.35\pm9.78$         & $165.16\pm4.54$         \\
% 91mNb & $\sigma_c$ & \hrulefill              & \hrulefill              & \hrulefill              & \hrulefill              & \hrulefill              & $66.96\pm4.16$          \\
% 92mNb & $\sigma_c$ & $42.18\pm1.15$          & $45.74\pm1.16$          & $48.75\pm1.21$          & $51.59\pm1.34$          & $54.49\pm1.37$          & $60.36\pm1.23$          \\
% 93mMo & $\sigma_c$ & $0.93\pm0.18$           & $1.25\pm0.13$           & $1.58\pm0.22$           & $1.80\pm0.12$           & $1.83\pm0.10$           & $2.010\pm0.084$         \\ \bottomrule
% \end{tabular}
% \end{table}

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}
\centering
\caption{Measured cross sections for the various \ce{^{nat}Cu}(p,x) reaction products observed in this work. Cumulative cross sections are designated as $\sigma_c$, independent cross sections are designated as $\sigma_i$.}
\label{tab:cu_rp_table}
\small
\resizebox{\textwidth}{!}{%
\begin{tabular}{@{}lllllll@{}}
\toprule
                            & \multicolumn{6}{c}{Production cross section (mb)}                                                                                                         \\ \cmidrule(l){2-7} 
E$_\text{p}$ (MeV)          & $89.74^{+0.48}_{-0.43}$ & $79.95^{+0.67}_{-0.64}$ & $70.17^{+0.91}_{-0.85}$ & $61.58^{+1.03}_{-0.98}$ & $52.10^{+1.25}_{-1.20}$ & $41.05^{+1.62}_{-1.54}$ \\ \midrule
\ce{^{51}Cr}\,($\sigma_c$)    & $0.888\pm0.058$         & $0.361\pm0.015$         & $0.440\pm0.019$         & $0.2949\pm0.0070$       & \hrulefill              & \hrulefill              \\
\ce{^{52}Mn}\,($\sigma_c$)    & $1.640\pm0.042$         & $0.552\pm0.014$         & $0.0398\pm0.0012$       & $0.00513\pm0.00051$     & \hrulefill              & \hrulefill              \\
\ce{^{52g}Mn}\,($\sigma_i$)   & $0.650\pm0.018$         & $0.231\pm0.013$         & $0.0160\pm0.0021$       & $0.000961\pm0.000027$   & \hrulefill              & \hrulefill              \\
\ce{^{52m}Mn}\,($\sigma_i$)   & $0.989\pm0.037$         & $0.321\pm0.020$         & $0.0238\pm0.0032$       & $0.00417\pm0.00043$     & \hrulefill              & \hrulefill              \\
\ce{^{54}Mn}\,($\sigma_c$)    & $5.67\pm0.15$           & $3.65\pm0.11$           & $4.05\pm0.11$           & $4.71\pm0.12$           & $1.656\pm0.042$         & \hrulefill              \\
\ce{^{55}Co}\,($\sigma_c$)    & $1.656\pm0.048$         & $0.983\pm0.030$         & $0.1892\pm0.0076$       & $0.0291\pm0.0024$       & $0.00231\pm0.00019$     & \hrulefill              \\
\ce{^{56}Ni}\,($\sigma_c$)    & $0.0779\pm0.0022$       & $0.0973\pm0.0025$       & $0.0886\pm0.0022$       & $0.02967\pm0.00079$     & \hrulefill              & \hrulefill              \\
\ce{^{57}Ni}\,($\sigma_c$)    & $1.416\pm0.039$         & $1.164\pm0.030$         & $1.370\pm0.033$         & $2.074\pm0.051$         & $1.543\pm0.035$         & $0.02638\pm0.00077$     \\
\ce{^{57}Co}\,($\sigma_i$)    & $38.78\pm0.99$          & $34.42\pm0.84$          & $35.06\pm0.81$          & $47.3\pm1.1$            & $47.0\pm1.1$            & $3.227\pm0.081$         \\
\ce{^{58}Co}\,($\sigma_c$)    & $55.7\pm3.5$            & $53.2\pm4.1$            & $41.8\pm2.9$            & $32.8\pm2.5$            & $38.4\pm3.4$            & $62.7\pm3.4$            \\
\ce{^{58g}Co}\,($\sigma_i$)   & $13.6\pm2.3$            & $10.5\pm1.9$            & $5.9\pm1.6$             & $7.6\pm1.3$             & $7.0\pm1.7$             & $1.13\pm0.31$           \\
\ce{^{58m}Co}\,($\sigma_i$)   & $42.2\pm2.7$            & $42.8\pm3.6$            & $35.8\pm2.5$            & $25.2\pm2.1$            & $31.5\pm2.9$            & $61.6\pm3.4$            \\
\ce{^{59}Fe}\,($\sigma_c$)    & $0.836\pm0.027$         & $0.810\pm0.022$         & $0.733\pm0.020$         & $0.601\pm0.017$         & $0.206\pm0.010$         & $0.93\pm0.15$           \\
\ce{^{60}Co}\,($\sigma_c$)    & $12.79\pm0.43$          & $13.04\pm0.42$          & $10.89\pm0.78$          & $11.15\pm0.58$          & $9.17\pm0.74$           & $6.7\pm1.0$             \\
\ce{^{61}Cu}\,($\sigma_c$)    & $48.8\pm1.5$            & $54.4\pm1.7$            & $63.7\pm2.1$            & $70.3\pm2.1$            & $79.5\pm2.7$            & $158.2\pm3.2$           \\
\ce{^{64}Cu}\,($\sigma_c$)    & $37.4\pm1.4$            & $41.4\pm1.2$            & $44.5\pm1.7$            & $49.0\pm1.5$            & $54.9\pm1.4$            & $63.7\pm1.6$            \\ \bottomrule
\end{tabular}
}
\end{table}
\caption{Measured cross sections for the various \ce{^{nat}Nb}(p,x) reaction products observed in this work. Cumulative cross sections are designated as $\sigma_c$, independent cross sections are designated as $\sigma_i$.}
\label{tab:nb_rp_table}
\small
\begin{tabular}{@{}lllllll@{}}
                            & \multicolumn{6}{c}{Production cross section (mb)}                                                                                                         \\ \cmidrule(l){2-7} 
E$_\text{p}$ (MeV)          & $89.37^{+0.47}_{-0.45}$ & $79.55^{+0.68}_{-0.64}$ & $69.70^{+0.90}_{-0.85}$ & $61.07^{+1.05}_{-0.98}$ & $51.51^{+1.25}_{-1.21}$ & $40.34^{+1.58}_{-1.55}$ \\ \midrule
\ce{^{82m}Rb}\,($\sigma_c$)   & $2.39\pm0.18$           & \hrulefill              & \hrulefill              & \hrulefill              & \hrulefill              & \hrulefill              \\
\ce{^{83}Sr}\,($\sigma_c$)    & $3.88\pm0.56$           & $4.63\pm0.34$           & $3.42\pm0.32$           & \hrulefill              & \hrulefill              & \hrulefill              \\
\ce{^{85}Y}\,($\sigma_c$)     & $13.31\pm0.30$          & $7.28\pm0.44$           & $2.06\pm0.12$           & \hrulefill              & \hrulefill              & \hrulefill              \\
\ce{^{85g}Y}\,($\sigma_i$)    & $2.286\pm0.057$         & $2.01\pm0.15$           & $0.545\pm0.030$         & \hrulefill              & \hrulefill              & \hrulefill              \\
\ce{^{85m}Y}\,($\sigma_i$)    & $11.03\pm0.30$          & $5.27\pm0.42$           & $1.52\pm0.12$           & \hrulefill              & \hrulefill              & \hrulefill              \\
\ce{^{86}Zr}\,($\sigma_c$)    & $12.25\pm0.32$          & $17.63\pm0.44$          & $18.86\pm0.43$          & $6.00\pm0.15$           & \hrulefill              & \hrulefill              \\
\ce{^{86}Y}\,($\sigma_i$)     & $32.25\pm0.89$          & $40.3\pm1.1$            & $39.0\pm1.0$            & $13.22\pm0.34$          & \hrulefill              & \hrulefill              \\
\ce{^{87}Zr}\,($\sigma_c$)    & $45.8\pm5.8$            & $27.1\pm1.7$            & $31.5\pm1.5$            & $48.5\pm2.9$            & $37.7\pm1.6$            & $1.13\pm0.10$           \\
\ce{^{87}Y}\,($\sigma_i$)     & $106.3\pm5.8$           & $52.9\pm1.7$            & $59.6\pm1.5$            & $87.8\pm2.9$            & $66.3\pm1.6$            & $2.93\pm0.10$           \\
\ce{^{87g}Y}\,($\sigma_i$)    & $27.0\pm5.4$            & $7.1\pm1.2$             & $6.41\pm0.55$           & $5.6\pm2.1$             & $2.59\pm0.45$           & $0.949\pm0.045$         \\
\ce{^{87m}Y}\,($\sigma_i$)    & $79.2\pm2.0$            & $45.8\pm1.2$            & $53.2\pm1.4$            & $82.1\pm2.0$            & $63.7\pm1.5$            & $1.983\pm0.093$         \\
\ce{^{88}Zr}\,($\sigma_c$)    & $153.7\pm3.9$           & $140.0\pm3.5$           & $61.0\pm1.7$            & $20.65\pm0.49$          & $33.16\pm0.97$          & $65.8\pm1.3$            \\
\ce{^{88}Y}\,($\sigma_i$)     & $16.64\pm0.76$          & $12.85\pm0.60$          & $7.81\pm0.61$           & $2.83\pm0.20$           & $9.0\pm1.3$             & $9.96\pm0.33$           \\
\ce{^{89}Nb}\,($\sigma_c$)    & \hrulefill              & \hrulefill              & $176\pm12$          & $209.0\pm4.3$           & \hrulefill              & \hrulefill              \\
\ce{^{89g}Nb}\,($\sigma_i$)   & \hrulefill              & \hrulefill              & $142\pm12$          & $181.7\pm4.1$           & \hrulefill              & \hrulefill              \\
\ce{^{89m}Nb}\,($\sigma_i$)   & \hrulefill              & \hrulefill              & $33.9\pm2.0$            & $27.3\pm1.4$            & \hrulefill              & \hrulefill              \\
\ce{^{89}Zr}\,($\sigma_i$)   & $203.8\pm5.3$           & $235.4\pm6.6$           & $287.5\pm6.8$           & $250.3\pm5.8$           & $54.6\pm1.1$            & $15.61\pm0.31$          \\
\ce{^{90}Mo}\,($\sigma_c$)    & $20.6\pm0.7$            & $25.58\pm0.76$          & $33.75\pm0.90$          & $60.4\pm1.9$            & $120.3\pm2.9$           & $24.38\pm0.71$          \\
\ce{^{90}Nb}\,($\sigma_i$)    & $152.9\pm4.7$           & $169.3\pm4.8$           & $204.7\pm5.8$           & $265.2\pm7.8$           & $363.4\pm9.8$           & $165.2\pm4.5$           \\
\ce{^{91m}Nb}\,($\sigma_c$)   & \hrulefill              & \hrulefill              & \hrulefill              & \hrulefill              & \hrulefill              & $67.0\pm4.2$            \\
\ce{^{92m}Nb}\,($\sigma_c$)   & $42.2\pm1.2$            & $45.7\pm1.2$            & $48.8\pm1.2$            & $51.6\pm1.3$            & $54.5\pm1.4$            & $60.4\pm1.2$            \\
\ce{^{93m}Mo}\,($\sigma_c$)   & $0.93\pm0.18$           & $1.25\pm0.13$           & $1.58\pm0.22$           & $1.80\pm0.12$           & $1.83\pm0.10$           & $2.010\pm0.084$         \\ \bottomrule
